An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-13 EconGrowthSeminar.Rnw
Fixed one remaining bug with the presentation after switching to energyType=NA signifying that a model without energy is desired.

\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %---------------------------- 
<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
createCDParamsGraph()
@  
\end{frame}

>>>>

\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %---------------------------- 
<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
createCDParamsGraph(energyType=NA)
@  
\end{frame}
